PM Component Paper Plots

### 2021-01-29 code/data-viz/plot-results.Rmd
added SE to all datasets - created config file for fac-EM runs- cleaned outputs- plot outputs

```{r Load data}
load(here('output','analysis','out-pmc-base.RDa'))
load(here('output','analysis','out-pmc-ses.RDa'))
load(here('output','analysis','out-fac-base.RDa'))
load(here('output','analysis','out-fac-ses.RDa'))

```

@@

data <- data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp),
         sig = ifelse(HR.U < 1 , '1-prtc',
                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos'))
         )
# #610038
plot_cols <- c("red")

@@

facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25, 'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  ) +
ggsave(here('output', 'plot','pmc-base.png'), width = 9.5, height = 7.5)
```

@@

facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25, 'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  ) +
ggsave(here('output', 'plot','pmc-ses.png'), width = 9.5, height = 7.5)
```

@@

data <- data %>% 
  filter(Index %in% So,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So),
         sig = ifelse(HR.U < 1 , '1-prtc',
                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos'))
         )
# #610038
plot_cols <- c("red")

@@

facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  ) +
ggsave(here('output', 'plot','fac-base.png'), width = 9.5, height = 5.5)
```

@@

facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  ) +
ggsave(here('output', 'plot','fac-ses.png'), width = 9.5, height = 5.5)
```

@@

facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  ) +
ggsave(here('output', 'plot','fac-ex-ec-base.png'), width = 9.5, height = 5.5)
```

@@

facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  ) +
ggsave(here('output', 'plot','fac-ex-ec-ses.png'), width = 9.5, height = 5.5)
```

```{r - Components - PM Residual}
data <- read_excel('Comp_PMResi.xlsx')

cmp <- c("-OC", "-NO3", "-V", "-Ni", "-SO4", "-Se",
         "-Zn", "-Pb", "-Ca", "-Si", "PM2.5")
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", 
         "Respiratory", "Pneumonia",
         "Cancer","Lung Cancer") # "CHF", "COPD",

@@

plot_cols <- c("red")

@@

facet_wrap( ~ Cause, ncol = 4, scales = "fixed") +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  ) +
ggsave("CMP_PMResi_1114.jpeg", width = 9.5, height = 5.5)
```

@@

```{r - Factor - PM Residual}
data <- read_excel('Fac_PMResi.xlsx')

So <- c("-Traffic", "-Oil", "-Coal", 
         "-Metals","-Soil", "PM2.5") # "-Steel", "-Salt", "-Biomass", 
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", 
         "Respiratory", "Pneumonia",
         "Cancer","Lung Cancer") # "CHF", "COPD",

@@

facet_wrap( ~ Cause, ncol = 4, scales = "fixed") +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  ) +
ggsave("Fac_PMResi_1114.jpeg", width = 9.5, height = 4.5)
```

```{r - Components Region}
data <- read_excel('Comp_Region.xlsx')

cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "Se", "SO4", 
          "Ni", "V", "NO3", "OC") 
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia", 
         "Cancer", "Lung Cancer")

@@

@@

ggsave("CMP_Region_1113.jpeg", p, width = 9.5, height = 12)
```

@@

```{r - Components Race}
data <- read_excel('Comp_Race.xlsx')

cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "Se", "SO4", 
          "Ni", "V", "NO3", "OC") 
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia", 
         "Cancer", "Lung Cancer")

@@

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0,0.25,0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
nrow = 2)

ggsave("CMP_Race_1113.jpeg", p, width = 9.5, height = 12)
```

@@

```{r Components Urban}
data <- read_excel('Comp_Urban.xlsx')

cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "Se", "SO4", 
          "Ni", "V", "NO3", "OC") 
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia", 
         "Cancer", "Lung Cancer")

@@

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25, 0, 0.25, 0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),

@@

facet_grid(Index ~ Cause,  scales = "fixed", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25, 0, 0.25, 0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
nrow = 2)

ggsave("CMP_Urban_1113.jpeg", p, width = 9.5, height = 10)
```

@@

```{r Components SES-Urban}
data <- read_excel('Comp_SESUrban.xlsx')

cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "Se", "SO4", 
          "Ni", "V", "NO3", "OC") 
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia", 
         "Cancer", "Lung Cancer")

@@

```{r - Components BRFSS}
data <- read_excel('Comp_BRFSS.xlsx')

cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "Se", "SO4", 
          "Ni", "V", "NO3", "OC") 
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia", 
         "Cancer", "Lung Cancer")

@@

```{r Components Buffer}
data <- read_excel('Comp_Buffer.xlsx')

>>>>

```{r Load data}
load(here('output','analysis','out-pmc-base.RDa'))
load(here('output','analysis','out-pmc-ses.RDa'))
load(here('output','analysis','out-fac-base.RDa'))
load(here('output','analysis','out-fac-ses.RDa'))
load(here('output','analysis','out-fac-ex-ec-base.RDa'))
load(here('output','analysis','out-fac-ex-ec-ses.RDa'))
load(here('output','analysis','out-pmc-resid.RDa'))
load(here('output','analysis','out-fac-resid.RDa'))
load(here('output','analysis','out-pmc-region.RDa'))
load(here('output','analysis','out-pmc-race.RDa'))
load(here('output','analysis','out-pmc-urbanicity.RDa'))
load(here('output','analysis','out-pmc-sescat.RDa'))
load(here('output','analysis','out-pmc-brfss.RDa'))
load(here('output','analysis','out-pmc-age.RDa'))
load(here('output','analysis','out-pmc-sex.RDa'))
load(here('output','analysis','out-pmc-buffer.RDa'))
load(here('output','analysis','out-pmc-expo.RDa'))
```

@@

plot_cols <- c("#D71A21")

@@

facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25, 'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  ) +
ggsave(here('output', 'plot','pmc-base.png'), width = 6.5, height = 8.5)
```

@@

facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25, 'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  ) +
ggsave(here('output', 'plot','pmc-ses.png'), width = 6.5, height = 8.5)
```

@@

data <- data %>% 
  filter(Index %in% So,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So),
         sig = ifelse(HR.U < 1 , '1-prtc',
                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos'))
         )

plot_cols <- c("#D71A21")

@@

facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  ) +
ggsave(here('output', 'plot','fac-base-ec.png'), width = 6.5, height = 8.5)
```

@@

facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  ) +
ggsave(here('output', 'plot','fac-ses-ec.png'), width = 6.5, height = 8.5)
```

@@

facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  ) +
ggsave(here('output', 'plot','fac-base.png'), width = 6.5, height = 8.5)
```

@@

facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  ) +
ggsave(here('output', 'plot','fac-ses.png'), width = 6.5, height = 8.5)
```

```{r - Components - PM Residual}
data <- out.pmc.resid

cmp <- c("-V", "-Ni","-Cl", "-Na", "-SO4", "-Se", "-OC", "-NO3", 
         "-Zn", "-Pb", "-Ca", "-Si", "PM2.5")
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia",
         "Cancer", "Lung Cancer")

@@

plot_cols <- c("#D71A21")

@@

facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  ) +
ggsave(here('output', 'plot','pmc-resid.png'), width = 6.5, height = 8.5)
```

@@

```{r - Factor - PM Residual}
data <- out.fac.resid

So <- c("-Oil", "-Salt", "-Coal", 
         "-Traffic", "-Metals", "-Soil", "PM2.5")
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia",
         "Cancer", "Lung Cancer")

@@

facet_wrap( ~ Cause, nrow = 2, scales = "fixed") +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  ) +
ggsave(here('output', 'plot','fac-resid.png'), width = 6.5, height = 8.5)
```

```{r - Components Region}
data <- out.pmc.region

cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
         "Na", "Cl", "Ni", "V") 
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia", 
         "Cancer", "Lung Cancer")

data <- data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp),
         Tag = ifelse(Region == "west", "d",
                      ifelse(Region == "midwest", "c",
                             ifelse(Region == "south", "b", "a"))),
         Tag = as.factor(Tag)
         )

@@

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0.25,0,0.25,0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),

@@

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0.25,0,0.25,0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10,face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
nrow = 2)

ggsave(here('output', 'plot','pmc-region.png'),p, width = 6.5, height = 8.5)
```

@@

```{r - Components Race}
data <- out.pmc.race

cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
         "Na", "Cl", "Ni", "V") 
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia", 
         "Cancer", "Lung Cancer")

data <- data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp),
         Tag = ifelse(Race == "A", "d",
                      ifelse(Race == "B", "c",
                             ifelse(Race == "H", "b", "a"))),
         Tag = as.factor(Tag)
         )

@@

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0.25,0,0.25,0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
nrow = 2)

ggsave(here('output', 'plot','pmc-race.png'),p, width = 6.5, height = 8.5)
```

```{r - Components Age}
data <- out.pmc.age

cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
         "Na", "Cl", "Ni", "V") 
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia", 
         "Cancer", "Lung Cancer")

data <- data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp),
         Tag = ifelse(Age == "LE75", "b", "a"),
         Tag = as.factor(Tag)
         )

plot_labs <- c("> 75 years", "<= 75 years")
plot_cols <- c("red", "blue")

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0.25,0,0.25,0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0.25,0,0.25,0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
nrow = 2)

ggsave(here('output', 'plot','pmc-age.png'),p, width = 6.5, height = 8.5)
```

```{r - Components Sex}
data <- out.pmc.sex

cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
         "Na", "Cl", "Ni", "V") 
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia", 
         "Cancer", "Lung Cancer")

data <- data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp),
         Tag = ifelse(Sex == "F", "b", "a"),
         Tag = as.factor(Tag)
         )

plot_labs <- c("Male", "Female")
plot_cols <- c("red", "blue")

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0.25,0,0.25,0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0.25,0,0.25,0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
nrow = 2)

ggsave(here('output', 'plot','pmc-sex.png'),p, width = 6.5, height = 8.5)
```

@@

```{r Components Urban}
data <- out.pmc.urbanicity

cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
         "Na", "Cl", "Ni", "V") 
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia", 
         "Cancer", "Lung Cancer")

data <- data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp),
         Tag = ifelse(Loc.Set == "urban", "b", "a"),
         Tag = as.factor(Tag)
         )

@@

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0.25,0,0.25,0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),

@@

facet_grid(Index ~ Cause,  scales = "fixed", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0.25,0,0.25,0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
nrow = 2)

ggsave(here('output', 'plot','pmc-urbanicity.png'),p, width = 6.5, height = 8.5)
```

@@

```{r Components SES-Urban}
data <- out.pmc.sescat

cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
         "Na", "Cl", "Ni", "V")
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia", 
         "Cancer", "Lung Cancer")

data <- data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp),
         Tag = ifelse(SES.Cat == "L", "c",
                      ifelse(SES.Cat == "M", "b", "a")),
         Tag = as.factor(Tag)
         )

@@

```{r - Components BRFSS}
data <- out.pmc.brfss

cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
         "Na", "Cl", "Ni", "V")
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia", 
         "Cancer", "Lung Cancer")

data <- data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp),
         Tag = ifelse(BRFSS == "brfss0", "b", "a"),
         Tag = as.factor(Tag)
         )

@@

```{r Components Buffer}
data <- out.pmc.buffer
